R for Clinical Study Reports and Submission

### 2021-09-02 tlf-ae-spec.Rmd
fix typo. reorg comments

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need to summarize which patients were included in each efficacy analysis 
in Section 12.2, aAdverse Events (AEs).

>>>>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need to summarize which patients were included in each efficacy analysis 
in Section 12.2, Adverse Events (AEs).
